Current and future constraints on primordial magnetic fields

### 2015-11-12 pmf.tex
summary of later chains

\begin{table*}[htb]
\begin{center}
\caption{\label{tab:param_all} All parameter constraints}
\tiny
\begin{tabular}{l || c c c c c c c | c}
Chain & $\Omega_b h^2$  & $\Omega_c h^2$  & $\theta$  & $\tau$  & logA  & $n_s$  & $A_{lens}$  & $A_{pmf}$ \\
lcdm\_alens\_all & $ 0.02240\pm  0.00026$ & $ 0.1179\pm  0.0020$ & $ 1.04106\pm  0.00047$ & $ 0.064\pm  0.016$ & $ 3.057\pm  0.030$ & $ 0.9696\pm  0.0062$ & $ 1.121 \pm  0.064$ & $< 0.33$ \\
lcdm\_alens\_nopmf\_all & $ 0.02241\pm  0.00024$ & $ 0.1179\pm  0.0020$ & $ 1.04106\pm  0.00047$ & $ 0.065\pm  0.016$ & $ 3.059\pm  0.029$ & $ 0.9694\pm  0.0062$ & $ 1.136 \pm  0.063$ & $< 0.00$ \\
lcdm\_alens\_nopmf\_planck & $ 0.02256\pm  0.00027$ & $ 0.1173\pm  0.0021$ & $ 1.04121\pm  0.00048$ & $ 0.069\pm  0.017$ & $ 3.067\pm  0.030$ & $ 0.9721\pm  0.0063$ & $ 1.175 \pm  0.067$ & $< 0.00$ \\
lcdm\_alens\_planckTT & $ 0.02252\pm  0.00031$ & $ 0.1174\pm  0.0027$ & $ 1.04122\pm  0.00053$ & $ 0.070\pm  0.050$ & $ 3.068\pm  0.098$ & $ 0.9713\pm  0.0080$ & $ 1.155 \pm  0.136$ & $< 1.34$ \\
lcdm\_alens\_planckTT\_TEB & $ 0.02264\pm  0.00029$ & $ 0.1161\pm  0.0025$ & $ 1.04141\pm  0.00053$ & $ 0.055\pm  0.021$ & $ 3.036\pm  0.042$ & $ 0.9755\pm  0.0072$ & $ 1.241 \pm  0.104$ & $< 0.77$ \\
lcdm\_alens\_planck & $ 0.02254\pm  0.00026$ & $ 0.1173\pm  0.0020$ & $ 1.04121\pm  0.00046$ & $ 0.068\pm  0.016$ & $ 3.065\pm  0.030$ & $ 0.9723\pm  0.0062$ & $ 1.171 \pm  0.070$ & $< 0.68$ \\
lcdm\_alens\_planck\_bicep & $ 0.02255\pm  0.00026$ & $ 0.1174\pm  0.0020$ & $ 1.04120\pm  0.00047$ & $ 0.069\pm  0.017$ & $ 3.067\pm  0.030$ & $ 0.9724\pm  0.0063$ & $ 1.177 \pm  0.068$ & $< 0.36$ \\
lcdm\_alens\_planck\_pb & $ 0.02255\pm  0.00027$ & $ 0.1173\pm  0.0021$ & $ 1.04119\pm  0.00046$ & $ 0.068\pm  0.017$ & $ 3.066\pm  0.031$ & $ 0.9725\pm  0.0064$ & $ 1.171 \pm  0.068$ & $< 0.63$ \\
lcdm\_alens\_planck\_sptpolB & $ 0.02254\pm  0.00026$ & $ 0.1173\pm  0.0020$ & $ 1.04121\pm  0.00047$ & $ 0.069\pm  0.017$ & $ 3.067\pm  0.030$ & $ 0.9724\pm  0.0062$ & $ 1.159 \pm  0.067$ & $< 0.42$ \\
lcdm\_alens\_planck\_sptpolE & $ 0.02239\pm  0.00025$ & $ 0.1178\pm  0.0020$ & $ 1.04107\pm  0.00048$ & $ 0.064\pm  0.016$ & $ 3.057\pm  0.030$ & $ 0.9698\pm  0.0061$ & $ 1.119 \pm  0.067$ & $< 0.73$ \\
lcdm\_planck & $ 0.02225\pm  0.00023$ & $ 0.1184\pm  0.0020$ & $ 1.04102\pm  0.00047$ & $ 0.066\pm  0.017$ & $ 3.062\pm  0.030$ & $ 0.9682\pm  0.0060$ & $ 0.000 \pm  0.000$ & $< 0.73$ \\
lcdm\_r\_alens\_all & $ 0.02240\pm  0.00025$ & $ 0.1178\pm  0.0020$ & $ 1.04107\pm  0.00046$ & $ 0.064\pm  0.016$ & $ 3.056\pm  0.029$ & $ 0.9702\pm  0.0062$ & $ 1.123 \pm  0.063$ & $< 0.27$ \\
\end{tabular}
\tablecomments{ 
Summary of results (will be trimmed for paper). 
} \normalsize
\end{center}
\end{table*}

>>>>

\begin{table*}[h]
\begin{center}
\caption{\label{tab:param_all} All parameter constraints}
\tiny
\begin{tabular}{l || c c c c c c c | c}
Chain & $\Omega_b h^2$  & $\Omega_c h^2$  & $\theta$  & $\tau$  & logA  & $n_s$  & $A_{lens}$  & $A_{pmf}$ \\
lcdm\_alens\_all & $ 0.02240\pm  0.00026$ & $ 0.1179\pm  0.0020$ & $ 1.04106\pm  0.00047$ & $ 0.064\pm  0.016$ & $ 3.057\pm  0.030$ & $ 0.9696\pm  0.0062$ & $ 1.121 \pm  0.064$ & $< 0.33$ \\
lcdm\_alens\_nopmf\_all & $ 0.02241\pm  0.00024$ & $ 0.1179\pm  0.0020$ & $ 1.04106\pm  0.00047$ & $ 0.065\pm  0.016$ & $ 3.059\pm  0.029$ & $ 0.9694\pm  0.0062$ & $ 1.136 \pm  0.063$ & $< 0.00$ \\
lcdm\_alens\_nopmf\_planck & $ 0.02256\pm  0.00027$ & $ 0.1173\pm  0.0021$ & $ 1.04121\pm  0.00048$ & $ 0.069\pm  0.017$ & $ 3.067\pm  0.030$ & $ 0.9721\pm  0.0063$ & $ 1.175 \pm  0.067$ & $< 0.00$ \\
lcdm\_alens\_planckTT & $ 0.02252\pm  0.00031$ & $ 0.1174\pm  0.0027$ & $ 1.04122\pm  0.00053$ & $ 0.070\pm  0.050$ & $ 3.068\pm  0.098$ & $ 0.9713\pm  0.0080$ & $ 1.155 \pm  0.136$ & $< 1.34$ \\
lcdm\_alens\_planckTT\_TEB & $ 0.02264\pm  0.00029$ & $ 0.1161\pm  0.0025$ & $ 1.04141\pm  0.00053$ & $ 0.055\pm  0.021$ & $ 3.036\pm  0.042$ & $ 0.9755\pm  0.0072$ & $ 1.241 \pm  0.104$ & $< 0.77$ \\
lcdm\_alens\_planck & $ 0.02254\pm  0.00026$ & $ 0.1173\pm  0.0020$ & $ 1.04121\pm  0.00046$ & $ 0.068\pm  0.016$ & $ 3.065\pm  0.030$ & $ 0.9723\pm  0.0062$ & $ 1.171 \pm  0.070$ & $< 0.68$ \\
lcdm\_alens\_planck\_bicep & $ 0.02255\pm  0.00026$ & $ 0.1174\pm  0.0020$ & $ 1.04120\pm  0.00047$ & $ 0.069\pm  0.017$ & $ 3.067\pm  0.030$ & $ 0.9724\pm  0.0063$ & $ 1.177 \pm  0.068$ & $< 0.36$ \\
lcdm\_alens\_planck\_pb & $ 0.02255\pm  0.00027$ & $ 0.1173\pm  0.0021$ & $ 1.04119\pm  0.00046$ & $ 0.068\pm  0.017$ & $ 3.066\pm  0.031$ & $ 0.9725\pm  0.0064$ & $ 1.171 \pm  0.068$ & $< 0.63$ \\
lcdm\_alens\_planck\_sptpolB & $ 0.02254\pm  0.00026$ & $ 0.1173\pm  0.0020$ & $ 1.04121\pm  0.00047$ & $ 0.069\pm  0.017$ & $ 3.067\pm  0.030$ & $ 0.9724\pm  0.0062$ & $ 1.159 \pm  0.067$ & $< 0.42$ \\
lcdm\_alens\_planck\_sptpolE & $ 0.02239\pm  0.00025$ & $ 0.1178\pm  0.0020$ & $ 1.04107\pm  0.00048$ & $ 0.064\pm  0.016$ & $ 3.057\pm  0.030$ & $ 0.9698\pm  0.0061$ & $ 1.119 \pm  0.067$ & $< 0.73$ \\
lcdm\_planck & $ 0.02225\pm  0.00023$ & $ 0.1184\pm  0.0020$ & $ 1.04102\pm  0.00047$ & $ 0.066\pm  0.017$ & $ 3.062\pm  0.030$ & $ 0.9682\pm  0.0060$ & $ 0.000 \pm  0.000$ & $< 0.73$ \\
lcdm\_r\_alens\_all & $ 0.02240\pm  0.00025$ & $ 0.1178\pm  0.0020$ & $ 1.04107\pm  0.00046$ & $ 0.064\pm  0.016$ & $ 3.056\pm  0.029$ & $ 0.9702\pm  0.0062$ & $ 1.123 \pm  0.063$ & $< 0.27$ \\
\end{tabular}
\tablecomments{ 
Summary of results (will be trimmed for paper). 
} \normalsize
\end{center}
\end{table*}

\begin{table*}[h]
\begin{center}
\caption{\label{tab:param_all} All parameter constraints}
\tiny
\begin{tabular}{l || c c c c c c c | c}
Chain & $\Omega_b h^2$  & $\Omega_c h^2$  & $\theta$  & $\tau$  & logA  & $n_s$  & $A_{lens}$  & $A_{pmf}$ \\
lcdm\_alens\_all\_bk14 & $ 0.02240\pm  0.00025$ & $ 0.1179\pm  0.0020$ & $ 1.04106\pm  0.00045$ & $ 0.065\pm  0.017$ & $ 3.058\pm  0.030$ & $ 0.9696\pm  0.0060$ & $ 1.131 \pm  0.061$ & $< 0.27$ \\
lcdm\_alens\_all\_bk14\_tensor & $ 0.02243\pm  0.00025$ & $ 0.1178\pm  0.0020$ & $ 1.04110\pm  0.00047$ & $ 0.066\pm  0.017$ & $ 3.060\pm  0.030$ & $ 0.9704\pm  0.0062$ & $ 1.142 \pm  0.060$ & $< 0.29$ \\
lcdm\_alens\_all\_bk14\_vector & $ 0.02240\pm  0.00025$ & $ 0.1181\pm  0.0019$ & $ 1.04107\pm  0.00046$ & $ 0.064\pm  0.016$ & $ 3.056\pm  0.029$ & $ 0.9687\pm  0.0061$ & $ 1.134 \pm  0.061$ & $< 0.68$ \\
lcdm\_alens\_nopmf\_all\_bk14 & $ 0.02244\pm  0.00025$ & $ 0.1179\pm  0.0020$ & $ 1.04109\pm  0.00046$ & $ 0.066\pm  0.016$ & $ 3.061\pm  0.029$ & $ 0.9700\pm  0.0060$ & $ 1.145 \pm  0.061$ & $< 0.00$ \\
lcdm\_alens\_planck\_bk14 & $ 0.02256\pm  0.00027$ & $ 0.1174\pm  0.0020$ & $ 1.04120\pm  0.00048$ & $ 0.069\pm  0.017$ & $ 3.068\pm  0.030$ & $ 0.9723\pm  0.0062$ & $ 1.188 \pm  0.066$ & $< 0.28$ \\
lcdm\_alens\_planck\_bk14\_tensor & $ 0.02257\pm  0.00026$ & $ 0.1173\pm  0.0020$ & $ 1.04121\pm  0.00047$ & $ 0.069\pm  0.017$ & $ 3.067\pm  0.030$ & $ 0.9727\pm  0.0060$ & $ 1.186 \pm  0.065$ & $< 0.29$ \\
lcdm\_alens\_planck\_bk14\_vector & $ 0.02241\pm  0.00029$ & $ 0.1180\pm  0.0021$ & $ 1.04114\pm  0.00048$ & $ 0.065\pm  0.017$ & $ 3.058\pm  0.030$ & $ 0.9670\pm  0.0074$ & $ 1.149 \pm  0.075$ & $< 4.64$ \\
lcdm\_all\_bk14 & $ 0.02223\pm  0.00021$ & $ 0.1182\pm  0.0018$ & $ 1.04113\pm  0.00049$ & $ 0.074\pm  0.014$ & $ 3.074\pm  0.024$ & $ 0.9686\pm  0.0055$ & $ 0.000 \pm  0.000$ & $< 0.35$ \\
lcdm\_all\_bk14\_tensor & $ 0.02220\pm  0.00024$ & $ 0.1186\pm  0.0019$ & $ 1.04100\pm  0.00047$ & $ 0.067\pm  0.016$ & $ 3.063\pm  0.029$ & $ 0.9672\pm  0.0057$ & $ 0.000 \pm  0.000$ & $< 0.31$ \\
lcdm\_all\_bk14\_vector & $ 0.02215\pm  0.00022$ & $ 0.1188\pm  0.0020$ & $ 1.04088\pm  0.00046$ & $ 0.064\pm  0.016$ & $ 3.056\pm  0.028$ & $ 0.9653\pm  0.0055$ & $ 0.000 \pm  0.000$ & $< 0.83$ \\
lcdm\_r\_alens\_all\_bk14 & $ 0.02242\pm  0.00025$ & $ 0.1175\pm  0.0021$ & $ 1.04111\pm  0.00048$ & $ 0.068\pm  0.018$ & $ 3.063\pm  0.032$ & $ 0.9710\pm  0.0063$ & $ 1.133 \pm  0.062$ & $< 0.24$ \\
\end{tabular}
\tablecomments{ 
Summary of results (will be trimmed for paper). 
} \normalsize
\end{center}
\end{table*}
